# Packages
* [nnet](http://cran.r-project.org/web/packages/nnet/nnet.pdf): NN with single hidden layer
* [neuralnet](http://cran.r-project.org/web/packages/neuralnet/neuralnet.pdf): training neural network

# nnet
## nnet: training via BFGS
* `nnet(formula, data, ...)`
* `nnet(x, y, size, rang, maxit, ...)`
    + `x`: input variables
    + `y`: output variables - instance of `class.ind()`
    + `range`: range for initial random weights. 
      Should be above 0.5 and `1/max(|x|)` if inputs are large.
    + `decay=0`: penalty for weights: $decay=10^{-3 \cdots 0}$ can avoid overfitting
    + `maxit=100`: maxium numbe of iterations for trainings
    + `linout=F`: linear activation function for regression
    + `softmax=F`: softmax activation function
        - generalization of logistic function to multiple classes
        - log-linear model
        - node probabilities will sum up to 1
          $$\delta_i=\frac{\exp{a_i}}{\sum_j \exp{a_j}}$$
          $$a_j=\sum_i x_i w_{i,j}$$

* Results
    + `value`: convergence criterion
    + `convergence`: `maxit` reached?
    + `wts`: weights

```{r cached=T, results='hide'}
library(nnet)
x <- subset(iris, select=-Species)
y <- class.ind(iris$Species)
while (T) {
  nn <- nnet(x, y, size=3, maxit=200, range=1/max(abs(x)), abstol=0, reltol=0)
  if (nn$value <= 2.0) {
    break
  }
}
```

## predict
* `predict.nn(nnet, x, type, ...)`
    + `type=raw`: matrix output
    + `type=class`: output most likely class. Only if `formula` was used

```{r}
p <- predict(nn, x)
table(max.col(y), max.col(p))
```


# neuralnet
## neuralnet
* trains neural network
* `neuralnet(formula, data, hidden, rep)`
    + `hidden=1`: number of hidden units
    + `rep=1`: training repetitions
    + `act.fct='logistic'`: activation function of string (logistic, tanh)
    + `linear.output=F`: do no apply activation function to output units
* still buggy

## AND/OR function
```{r, cached=T, results='hide'}
library(neuralnet)
binary.data <- data.frame(expand.grid(c(0,1), c(0,1), c(0,1)), AND, OR)
net <- neuralnet(AND+OR~Var1+Var2+Var3, binary.data, hidden=0, rep=10)
print(net)
plot(net, rep='best')
```
